\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-03-11 popl-2019-journal-v/paper.tex
rephrase title
Reword a phrase about differences with the conference version.

\begin{jversion}
  This text is an extended version of a paper that was presented at POPL 2019~\citep{skorstengaard_stktokens_2019}.
  Compared to the earlier text, this version adds and explains aspects of our work that were left out in the conference version due to space restrictions.
  The added details include a better motivation of sealing (\sectionname~\ref{sec:purpose-sealing}), the requirements of well-formedness (\sectionname~\ref{sec:well-form-reas}) and reasonability of components (\sectionname~\ref{sec:reasonable-components}).
  The section on proving full-abstraction (\sectionname~\ref{sec:fa-proof}) has been rewritten with details and explanations about the formal method used for the full-abstraction proof.
  This includes a description and motivation of the Kripke world (\sectionname~\ref{subsec:worlds}) and logical relation (\sectionname~\ref{subsec:logical-relation}).
  This paper is accompanied by a technical report~\citep{technical_report_popl} with technical details and proofs.
\end{jversion}
% Notes on new contributions (based on the journal version environment):
% More details about the definition of the cap. machine (decoding/encoding functions)
% Well-formedness definitions
% Reasonability definition
% Expanded discussion section
% More detailed description of worlds and
%   the logical relation used

@@

\section{World Construction: solving the recursive domain equation}
\label{subsubsec:rec-dom-eq}
In the previous sections, we sketched what our worlds should be.
However, the worlds we want constitute a self-referential domain equation for which no solution exists in set and domain theory.
% Move to a different domain
Therefore, we need to move to a different domain with enough structure for a solution to exist for recursive equations.
Solutions to recursive domain equations can be found using standard techniques~\citep{scott_1976,america_1989,Birkedal:2011:SKM:1926385.1926401}.
Essentially, we move to a setting where instead of sets we have c.o.f.e.'s (complete ordered families of equivalences), instead of functions we have non-expansive functions, and instead of relations we have downwards-closed relations.
A c.o.f.e.\ can be thought of as a set with added structure.
Specifically, c.o.f.e.'s have a step-index that must satisfy a set of conditions which provide sufficient structure for a solution to exist for the recursive domain equation.

>>>>

\begin{jversion}
  This text is an extended version of a paper that was presented at POPL 2019~\citep{skorstengaard_stktokens_2019}.
  Compared to the earlier text, this version adds and explains aspects of our work that were left out in the conference version due to space restrictions.
  The added details include a better motivation of sealing (\sectionname~\ref{sec:purpose-sealing}), the requirements of well-formedness (\sectionname~\ref{sec:well-form-reas}) and reasonability of components (\sectionname~\ref{sec:reasonable-components}).
  The section on proving full-abstraction (\sectionname~\ref{sec:fa-proof}) has been rewritten to better explain the method used for the full-abstraction proof.
  This includes a description and motivation of the Kripke worlds (\sectionname~\ref{subsec:worlds}) and logical relation (\sectionname~\ref{subsec:logical-relation}) that we use to do this.
  This paper is accompanied by a technical report~\citep{technical_report_popl} with technical details and proofs.
\end{jversion}
% Notes on new contributions (based on the journal version environment):
% More details about the definition of the cap. machine (decoding/encoding functions)
% Well-formedness definitions
% Reasonability definition
% Expanded discussion section
% More detailed description of worlds and
%   the logical relation used

@@

\section{Constructing Worlds: Solving the Recursive Domain Equation}
\label{subsubsec:rec-dom-eq}
In the previous sections, we sketched what our worlds should be.
However, the worlds we want constitute a self-referential domain equation for which no solution exists in set and domain theory.
% Move to a different domain
Therefore, we need to move to a different domain with enough structure for a solution to exist for recursive equations.
Solutions to recursive domain equations can be found using standard techniques~\citep{scott_1976,america_1989,Birkedal:2011:SKM:1926385.1926401}.
Essentially, we move to a setting where instead of sets we have c.o.f.e.'s (complete ordered families of equivalences), instead of functions we have non-expansive functions, and instead of relations we have downwards-closed relations.
A c.o.f.e.\ can be thought of as a set with added structure.
Specifically, c.o.f.e.'s have a step-index that must satisfy a set of conditions which provide sufficient structure for a solution to exist for the recursive domain equation.
